### 2022-09-28 Thesis/text/einleitung.tex
modification to line spacing, changed bt pictures
fertig?!

Mobile robots are becoming more widespread in many domains. They are marketed as autonomous mobile robots, but their autonomy is often limited to particular environments and requires frequent human help to function correctly. This reliance on a human operator hardly qualifies the robot to be labeled autonomous.

One of the quickest and most popular ways to build and program a robot is to use the Robot Operating System (ROS). ROS offers many tools and functionalities to create and program robots, but a standard robot needs human supervision during the operation to ensure proper function and safety. There are ROS packages to safely navigate from point A to point B, but currently, typical robots cannot react to unforeseen events. The robot needs to be able to navigate in an uncertain environment to guarantee the safety of the robot itself and all other actors in its environment. These can be either other robots or humans.

In theory, the robot can perform fully autonomous navigation, including mapping and localization. However, when something unexpected happens, the robot's autonomy can not be guaranteed any more. A default robot cannot represent all possible fail states and does not detect failures on a systematic level but only inside its navigation-related subsystems. Moreover, when failures inside these subsystems are discovered, the options to handle these problems are minimal and often do not deal with the problems in an autonomous way. The reliance on external problem-solving decreases the robot's usefulness when tasked with tangible goals. 
Therefore, this thesis centers around the research question of how behavior planning can increase the robustness and autonomy of a robot running ROS2. Behavior planning enables the robot to react to failures and problems of the system and can decide alternative courses of action to mitigate risks and finish the given tasks.

@@

	\item Chapter \ref{cha:methoden} compares the current systems and derives requirements from the key problem areas

>>>>

Mobile robots are becoming more widespread in many domains, like warehouse logistics, last-mile delivery, and agriculture. They are marketed as autonomous mobile robots, but their autonomy is often limited to particular environments and requires frequent human help to function correctly. This reliance on a human operator hardly qualifies the robot to be labeled autonomous.

One of the quickest and most popular ways to build and program a robot is to use the Robot Operating System (ROS). ROS offers many tools and functionalities to create and program robots, but a standard robot needs human supervision during the operation to ensure proper function and safety. The robot needs to be able to navigate in an uncertain environment to guarantee the safety of the robot itself and all other actors in its environment. There are ROS packages to enable safe navigation capabilities, but currently, typical ROS-based robots cannot react to unforeseen events.

In theory, the robot can perform fully autonomous navigation, including mapping and localization. However, when something unexpected happens, the robot's autonomy can not be guaranteed. A default robot cannot represent all possible fail states and does not detect failures on a systematic level but only inside its navigation-related subsystems. Moreover, when failures inside these subsystems are discovered, the options to handle these problems are minimal and often do not deal with the problems in an autonomous way. The reliance on external problem-solving decreases the robot's usefulness when tasked with tangible goals. 
Therefore, this thesis centers around the research question of how behavior planning can increase the robustness and autonomy of a robot running ROS2. Behavior planning enables the robot to react to failures and problems of the system and can decide alternative courses of action to mitigate risks and finish the given tasks.

@@

	\item Chapter \ref{cha:methoden} analyzes the current robotic systems and derives requirements from the key problem areas
